### 2012-06-28 inst/examples/bh_uniform.Rmd
exploring conditions responsible for noise becoming more or less cautious than deterministic

`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="bh_uniform/", verbose=TRUE or`

@@

  SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=2e5)
  opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                       profit, delta, reward=0)
}
````

>>>>

`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="bh_uniform_fast/", verbose=TRUE or`

@@

  SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=2e4)
  opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                       profit, delta, reward=0)
}
````
